Stage-structured evolutionary demography for simultaneous hermaphrodites with partial selfing

### 2020-08-31 notes/notes-SA-partSelf-wDemography.tex
Updated FunnelFig(), started cal. eigenvalue in fwdDemModelSim()
added zeta_i function, calculate in simulations

% Change default margins
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

@@

\newpage
% \begin{landscape}
% \begin{align*} \label{eq:AtildeCoexistence}
% 	\tilde{\mbf{A}}[\tilde{\mbf{n}}] &= \tilde{\mbf{U}} + \tilde{\mbf{F}}\\
% 		&= \left(
% 			\begin{array}{cc|cc|cc}
% 				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
% 				\mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\\hline
% 				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa} & \mbf{0} &  \mbf{0}\\\hline
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} \\ 
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa}
% 			\end{array} \right) \\ 
% 		&+ \left(
% 			\begin{array}{cc|cc|cc}
% 				C_{AA} (1 - \delta) \mbf{F}_{AA} & C_{AA} (1 - \delta) \mbf{F}_{AA}  & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} \\ 
% 				q^{\prime}_{A}  (1 - C_{AA}) \mbf{F}_{AA}& q^{\prime}_{A} (1 - C_{AA}) \mbf{F}_{AA} & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \mbf{0} & \mbf{0} \\ \hline
% 				\mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}& \mbf{0} & \mbf{0} \\
% 				q^{\prime}_{a} (1 - C_{AA}) \mbf{F}_{AA} & q^{\prime}_{a}(1 - C_{AA})  \mbf{F}_{AA} & \frac{1}{2}  (1 - C_{Aa}) \mbf{F}_{Aa}& \frac{1}{2} (1 - C_{Aa})\mbf{F}_{Aa} & q^{\prime}_{A} (1 - C_{aa})\mbf{F}_{aa}  & q^{\prime}_{A}  (1 - C_{aa})\mbf{F}_{aa}\\ \hline
% 				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} &  C_{aa} (1 - \delta) \mbf{F}_{aa}\\ 
% 				\mbf{0} & \mbf{0} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa}) \mbf{F}_{Aa} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa})\mbf{F}_{Aa}& q^{\prime}_{a}(1 - C_{aa})  \mbf{F}_{aa} & q^{\prime}_{a} (1 - C_{aa})\mbf{F}_{aa} 
% 			\end{array} \right) \numberthis
% \end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{thebibliography}{}

\bibitem[{Chang and Kirkpatrick(2018)Chang and Kirkpatrick}]{ChangKirkpatrick2018}
Chang, C., and M.~Kirkpatrick. 2018.
\newblock Inversions are bigger on the X chromosome.
\newblock Mol.~Ecol. 2018:1--8.

\bibitem[{Charlesworth et.~al.(1987)Charlesworth et.~al.}]{CharlesworthBarton1987}
Charlesworth, B., J.~A. Coyne, and N. Barton. 1987.
\newblock The relative rates of evolution of sex chromosomes and autosomes.
\newblock American Naturalist 130:113--146.

\bibitem[{Connallon et al.(2018)Connallon et al.}]{ConnallonOlito2018}
Connallon, T., C.~Olito, L.~Dutoit, H.~Popali, F.~Ruzicka, and L. Yong. 2018.
\newblock Local adaptation and the evolution of inversions on sex chromosomes and autosomes.
\newblock Phil.~Trans.~Roy.~Soc.~B 373:20170423.

\bibitem[{Orr(2000)Orr}]{Orr2000}
Orr, H.~A. 2000.
\newblock The rate of adaptation in asexuals.
\newblock Genetics 155:961--968.

\bibitem[{Orr and Kim(1998)Orr and Kim}]{OrrKim1998}
Orr, H.~A. and Y.~Kim. 1998.
\newblock An adaptive hypothesis for the evolution of the Y chromosome.
\newblock Genetics 150:1693--1698.

\end{thebibliography}

\end{document}

>>>>

% Change default margins
\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}

@@

%\newpage
% \begin{landscape}
% \begin{align*} \label{eq:AtildeCoexistence}
% 	\tilde{\mbf{A}}[\tilde{\mbf{n}}] &= \tilde{\mbf{U}} + \tilde{\mbf{F}}\\
% 		&= \left(
% 			\begin{array}{cc|cc|cc}
% 				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
% 				\mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\\hline
% 				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa} & \mbf{0} &  \mbf{0}\\\hline
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} \\ 
% 				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa}
% 			\end{array} \right) \\ 
% 		&+ \left(
% 			\begin{array}{cc|cc|cc}
% 				C_{AA} (1 - \delta) \mbf{F}_{AA} & C_{AA} (1 - \delta) \mbf{F}_{AA}  & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} \\ 
% 				q^{\prime}_{A}  (1 - C_{AA}) \mbf{F}_{AA}& q^{\prime}_{A} (1 - C_{AA}) \mbf{F}_{AA} & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \mbf{0} & \mbf{0} \\ \hline
% 				\mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}& \mbf{0} & \mbf{0} \\
% 				q^{\prime}_{a} (1 - C_{AA}) \mbf{F}_{AA} & q^{\prime}_{a}(1 - C_{AA})  \mbf{F}_{AA} & \frac{1}{2}  (1 - C_{Aa}) \mbf{F}_{Aa}& \frac{1}{2} (1 - C_{Aa})\mbf{F}_{Aa} & q^{\prime}_{A} (1 - C_{aa})\mbf{F}_{aa}  & q^{\prime}_{A}  (1 - C_{aa})\mbf{F}_{aa}\\ \hline
% 				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} &  C_{aa} (1 - \delta) \mbf{F}_{aa}\\ 
% 				\mbf{0} & \mbf{0} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa}) \mbf{F}_{Aa} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa})\mbf{F}_{Aa}& q^{\prime}_{a}(1 - C_{aa})  \mbf{F}_{aa} & q^{\prime}_{a} (1 - C_{aa})\mbf{F}_{aa} 
% 			\end{array} \right) \numberthis
% \end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
